Leveraged Volume Sampling - Summary

### 2019-03-02 summary/paper-summary.tex
added a brief on the proof of theorem 9

>>>>

        The proof of the second property is more complex but at it's core it builds on a lemma (proved in the paper) that states that if
        you sub-sample a set $T$ fixed number of rows uniformly without replacement from $m$ rows sampled via \textit{Leveraged Volume Sampling}
        then you can bound the following:
        \begin{equation}
            P(\lambda_{min}(\frac{1}{|T|}U^TQ_{\pi_{T}}U) \leq \frac{1}{4}) \leq \delta
        \end{equation}
        Then, they procede to generate such a uniform set $T$ and a standard volume-sampled $S$ of size $k$ out of $[m]$ where $T \subseteq S$.
        With high probability $|S \setminus T|=\mathcal{O}(d\log(d/\delta))$ and this in turn allows us to generate the bound in the second property.
        To prove this property the paper makes use of three lemmas where they use Tchernoff bounds on matrices as an important tool.
